---
title: "Project2InitialCleaning"
output:
  html_notebook: Project2InitialCLeaning
---

```{r}
library(car)
library(caTools)
library(ggplot2)
library(gridExtra)
library(leaps)
library(MASS)
library(pls)
library(plyr)
library(randomForest)
library(wesanderson)

options(stringsAsFactors = FALSE)
setwd("/Users/gatliffe/Documents/In Process/ASM Project 2")
Telco <- read.csv('WA_Fn-UseC_-Telco-Customer-Churn.csv')
#str(Telco)

colnames(Telco)[colnames(Telco)=="gender"] <- "Gender"
colnames(Telco)[colnames(Telco)=="tenure"] <- "Tenure"

#Remove ID
Telco <- Telco[-c(1)]

sapply(Telco, function(x) sum(is.na(x)))
#Remove NAs
Telco <- Telco[complete.cases(Telco), ] 

#Remove no internet service rows
Telco<- subset(Telco, Telco$OnlineSecurity != "No internet service") 
#Change no phone service to no
Telco$MultipleLines <- as.factor(mapvalues(Telco$MultipleLines, 
    from=c("No phone service"), to=c("No")))
Telco$SeniorCitizen <- as.factor(mapvalues
  (Telco$SeniorCitizen, from=c("0","1"), to=c("No", "Yes")))

summary(Telco)
```
 
 Setting Up Train and Test, Train is sample=True
 
```{r}
set.seed(1420)
Telco$sample = sample.split(Telco$Churn, SplitRatio = .75)
```

Check Correlations on train set only

```{r}
library(corrplot)
numeric.var <- sapply(Telco, is.numeric) 
trainset = subset(Telco, Telco$sample == TRUE)
cors<-cor(trainset[,numeric.var])  
corrplot(cors)
 Telco$FixedCharges<-NA
for(i in 1:nrow(Telco))
{
 Telco$FixedCharges[i]<-Telco$TotalCharges[i]-(Telco$MonthlyCharges[i]*Telco$Tenure[i]) 
}
numeric.var <- sapply(Telco, is.numeric) 
trainset = subset(Telco, Telco$sample == TRUE)
cors<-cor(trainset[,numeric.var])  
corrplot(cors)
```

TotalCharges has high correlations.

```{r}
trainset = subset(Telco, Telco$sample == TRUE)
```

Plots

```{r}
color=wes_palette("Zissou1",n=2)

plot1<-ggplot(data=trainset, aes(x=factor(Gender)))+ggtitle("Gender")+geom_bar(width=0.7, fill=color)+ coord_flip()
plot2<-ggplot(data=trainset, aes(x=factor(SeniorCitizen)))+ggtitle("Senior Citizen")+geom_bar(width=0.7, fill=color)+ coord_flip()  
plot3<-ggplot(data=trainset, aes(x=factor(Partner)))+ ggtitle("Partner")+geom_bar(width=0.7, fill=color)+ coord_flip()
plot4<-ggplot(data=trainset, aes(x=factor(Dependents)))+ ggtitle("Dependents")+geom_bar(width=0.7, fill=color) + coord_flip()    
plot5 <- ggplot(data=trainset, aes(x=PhoneService)) + ggtitle("Phone Service") +geom_bar(width=0.7, fill=color)+ coord_flip()
plot6 <- ggplot(data=trainset, aes(x=MultipleLines)) + ggtitle("Multiple Lines")+geom_bar(width=0.7, fill=color)+ coord_flip()
grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2)

plot7 <- ggplot(data=trainset, aes(x=InternetService)) + ggtitle("Internet Service") +geom_bar(width=0.7, fill=color)+ coord_flip()
plot8 <- ggplot(data=trainset, aes(x=OnlineSecurity)) + ggtitle("Online Security") + geom_bar(width=0.7, fill=color)+ coord_flip()
plot9 <- ggplot(trainset, aes(x=OnlineBackup)) + ggtitle("Online Backup")  +geom_bar(width=0.7, fill=color) + coord_flip() 
plot10 <- ggplot(trainset, aes(x=DeviceProtection)) + ggtitle("Device Protection") +geom_bar(width=0.7, fill=color) + coord_flip() 
plot11 <- ggplot(trainset, aes(x=TechSupport)) + ggtitle("Tech Support") +geom_bar(width=0.7, fill=color) + coord_flip() 
plot12 <- ggplot(trainset, aes(x=StreamingTV)) + ggtitle("Streaming TV") +geom_bar(width=0.7, fill=color) + coord_flip() 
grid.arrange(plot7, plot8, plot9, plot10, plot11, plot12, ncol=2)

plot13 <- ggplot(trainset, aes(x=StreamingMovies)) + ggtitle("Streaming Movies")+geom_bar(width=0.7, fill=color) + coord_flip()
color=wes_palette("Zissou1",n=3)
plot14 <- ggplot(trainset, aes(x=Contract)) + ggtitle("Contract") +geom_bar(width=0.7, fill=color) + coord_flip() 
color=wes_palette("Zissou1",n=2)
plot15 <- ggplot(trainset, aes(x=PaperlessBilling)) + ggtitle("Paperless Billing")+geom_bar(width=0.7, fill=color) + coord_flip() 
color=wes_palette("Zissou1",n=4)
plot16 <- ggplot(trainset, aes(x=PaymentMethod)) + ggtitle("Payment Method")+geom_bar(width=0.7, fill=color) + coord_flip() 

trainset$TenureCat<-NA

trainset$TenureCat[trainset$Tenure <= 6] <- "00-06M"
trainset$TenureCat[trainset$Tenure > 6 & trainset$Tenure <= 12] <- "06-12M"
trainset$TenureCat[trainset$Tenure > 12 & trainset$Tenure <= 24] <- "12-24M"
trainset$TenureCat[trainset$Tenure > 24] <- "24+M"
trainset$TenureCat<-factor(trainset$TenureCat)

color=wes_palette("Zissou1",n=4)
plot17 <- ggplot(trainset, aes(x=TenureCat)) + ggtitle("Tenure Group")+geom_bar(width=0.7, fill=color) + coord_flip() 

grid.arrange(plot13, plot14, plot15, plot16,plot17, ncol=2)
```

```{r}
Telco$Churn<-as.numeric(mapvalues
(Telco$Churn, from=c("No","Yes"), to=c("0","1")))
Telco$Gender <-   as.numeric(mapvalues
(Telco$Gender, from=c("Female","Male"), to=c("0","1")))
Telco$SeniorCitizen<-as.numeric(mapvalues
(Telco$SeniorCitizen, from=c("No","Yes"), to=c("0","1")))
Telco$Partner<-as.numeric(mapvalues
(Telco$Partner, from=c("No","Yes"), to=c("0","1")))
Telco$Dependents<-as.numeric(mapvalues
(Telco$Dependents, from=c("No","Yes"), to=c("0","1")))
Telco$PhoneService<-as.numeric(mapvalues
(Telco$PhoneService, from=c("No","Yes"), to=c("0","1")))
Telco$MultipleLines<-as.numeric(mapvalues
(Telco$MultipleLines, from=c("No","Yes"), to=c("0","1")))
Telco$InternetService<-as.numeric(mapvalues
(Telco$InternetService, from=c("DSL","Fiber optic"), to=c("0","1")))
Telco$OnlineSecurity<-as.numeric(mapvalues
(Telco$OnlineSecurity, from=c("No","Yes"), to=c("0","1")))
Telco$OnlineBackup <-as.numeric(mapvalues
(Telco$OnlineBackup, from=c("No","Yes"), to=c("0","1")))
Telco$PaperlessBilling <-as.numeric(mapvalues
(Telco$PaperlessBilling, from=c("No","Yes"), to=c("0","1")))
Telco$DeviceProtection<-as.numeric(mapvalues
(Telco$DeviceProtection, from=c("No","Yes"), to=c("0","1")))
Telco$TechSupport<-as.numeric(mapvalues
(Telco$TechSupport, from=c("No","Yes"), to=c("0","1")))
Telco$StreamingTV<-as.numeric(mapvalues
(Telco$StreamingTV, from=c("No","Yes"), to=c("0","1")))
Telco$StreamingMovies <-as.numeric(mapvalues
(Telco$StreamingMovies, from=c("No","Yes"), to=c("0","1")))
summary(Telco)
```

Dummy Variables for Tenure Category

```{r}

Telco$TenureCat.00.06<-0
Telco$TenureCat.06.12<-0
Telco$TenureCat.12.24<-0

Telco$TenureCat.00.06[Telco$Tenure <= 6] <- 1
Telco$TenureCat.06.12[Telco$Tenure > 6 & Telco$Tenure <= 12] <- 1
Telco$TenureCat.12.24[Telco$Tenure > 12 & Telco$Tenure <= 24] <- 1
```

Dummies for Payment Method, Contract

```{r}
Telco$OneYearContract<-0
Telco$TwoYearContract<-0

Telco$BankTransfer<-0
Telco$CreditCard<-0
Telco$ECheck<-0

Telco$OneYearContract[Telco$Contract == "One year"] <- 1
Telco$TwoYearContract[Telco$Contract == "Two year"] <- 1
Telco$Contract<-as.numeric(mapvalues
(Telco$Contract, from=c("Month-to-month","One year","Two year"), to=c("0","1","1")))

Telco$BankTransfer[Telco$PaymentMethod == "Bank transfer (automatic)"] <- 1
Telco$CreditCard[Telco$PaymentMethod == "Credit card (automatic)"] <- 1
Telco$ECheck[Telco$PaymentMethod == "Electronic check"] <- 1

summary(Telco)
```

Reorder for Clarity

```{r}
Telco<-Telco[c(21,20,1:16,18:19,22:30)]
View(Telco)
write.csv(Telco, file = 'TelcoMain.csv',row.names=FALSE)
``` 


Chi Squared

```{r include=FALSE}
trainsetChiSQ = subset(Telco, Telco$sample == TRUE)

trainsetChiSQ<-trainsetChiSQ[-c(1)]
for (i in 1:16)
{  
  k=i+1
  for (j in k:17)
{
    print(paste( i,"and", j))
    tbl = table(trainsetChiSQ[,i], trainsetChiSQ[,j])
        print(chisq.test(tbl,simulate.p.value = TRUE))
}
}
```

The chisq show a lot of colinearity.  

Splitting out test.

```{r}
trainset = subset(Telco, Telco$sample == TRUE)
testset  = subset(Telco, Telco$sample == FALSE)
trainset <-trainset[c(-1)]
testset <-testset[c(-1)]
```

Logistic AIC Model Function

```{r}

LogisticAIC<-function(trainset, testset)
{
 LogisticModel <- glm(as.factor(Churn) ~.,family=binomial(link="logit"),data=trainset)
summary(LogisticModel)
anova(LogisticModel, test="Chisq")

#AIC Selection 

mean_train<-apply(trainset, 2, mean)
var_train<-apply(trainset, 2, var)

train <- t((t(trainset)-mean_train)/sqrt(var_train))
apply(train, 2, mean)
apply(train, 2, var)

dat.train<-data.frame(train, Churn=trainset$Churn)
dat.train<-dat.train[c(-1)]

#Apply training mean and variance#

test <- t((t(testset)-mean_train)/sqrt(var_train))
dat.test <- data.frame(test, Churn=testset$Churn)
apply(test, 2, mean)
apply(test, 2, var)

LogisticModel.int <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="logit"), data=dat.train)
LogisticModel.full <- glm(as.factor(Churn.1) ~ ., family=binomial(link="logit"),  data=dat.train)

#Stepwise Selection AIC

X<-stepAIC(LogisticModel.int, direction="both",
             scope=list(lower=LogisticModel.int, upper= LogisticModel.full))
return()
}
```

Logistic BIC Model Function

```{r}
#Stepwise Selection BIC
LogisticBIC<-function(trainset, testset)
{
 LogisticModel <- glm(as.factor(Churn) ~.,family=binomial(link="logit"),data=trainset)
summary(LogisticModel)
anova(LogisticModel, test="Chisq")

mean_train<-apply(trainset, 2, mean)
var_train<-apply(trainset, 2, var)

train <- t((t(trainset)-mean_train)/sqrt(var_train))
apply(train, 2, mean)
apply(train, 2, var)

dat.train<-data.frame(train, Churn=trainset$Churn)
dat.train<-dat.train[c(-1)]

#Apply training mean and variance#

test <- t((t(testset)-mean_train)/sqrt(var_train))
dat.test <- data.frame(test, Churn=testset$Churn)
apply(test, 2, mean)
apply(test, 2, var)

LogisticModel.int <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="logit"), data=dat.train)
LogisticModel.full <- glm(as.factor(Churn.1) ~ ., family=binomial(link="logit"),  data=dat.train)

  stepAIC(LogisticModel.int, direction="both", k=log(1378),
             scope=list(lower=LogisticModel.int, upper= LogisticModel.full), criterion = "BIC")
}
```

```{r}
ProbitAIC<-function(trainset, testset)
{
mean_train<-apply(trainset, 2, mean)
var_train<-apply(trainset, 2, var)

train <- t((t(trainset)-mean_train)/sqrt(var_train))
apply(train, 2, mean)
apply(train, 2, var)

dat.train<-data.frame(train, Churn=trainset$Churn)
dat.train<-dat.train[c(-1)]

ProbitModel <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="probit"),data=dat.train)
summary(ProbitModel)
anova(ProbitModel, test="Chisq")

ProbitModel.int <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="probit"),data=dat.train)
ProbitModel.full <- glm(as.factor(Churn.1) ~ ., family=binomial(link="probit"),data=dat.train)

stepAIC(ProbitModel.int, direction="both",
             scope=list(lower=ProbitModel.int, upper= ProbitModel.full))
return()
}
```

```{r}
ProbitBIC<-function(trainset, testset)
{
mean_train<-apply(trainset, 2, mean)
var_train<-apply(trainset, 2, var)

train <- t((t(trainset)-mean_train)/sqrt(var_train))
apply(train, 2, mean)
apply(train, 2, var)

dat.train<-data.frame(train, Churn=trainset$Churn)
dat.train<-dat.train[c(-1)]

ProbitModel <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="probit"),data=dat.train)
summary(ProbitModel)
anova(ProbitModel, test="Chisq")

ProbitModel.int <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="probit"),data=dat.train)
ProbitModel.full <- glm(as.factor(Churn.1) ~ ., family=binomial(link="probit"),data=dat.train)
stepAIC(ProbitModel.int, direction="both", k=log(1378),
             scope=list(lower=ProbitModel.int, upper= ProbitModel.full), criterion = "BIC")
return()
}

```


```{r}
ErrorTesting<-function(Model, testset)
{
summary(Model)
anova(Model, test="Chisq")

fitted.results <- predict(Model,newdata=testset,type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)
misClasificError <- mean(fitted.results != testset$Churn)
print(1-misClasificError)
table(testset$Churn, fitted.results > 0.5)
exp(cbind(OR=coef(Model), confint(Model)))

return()
}
```

mfxboot is a function for bootstrapping Logit and Probit and was found here:
https://diffuseprior.wordpress.com/2012/04/23/probitlogit-marginal-effects-in-r-2/

```{r}
mfxboot <- function(modform,dist,data,boot=500,digits=3){
  x <- glm(modform, family=binomial(link=dist),data)
  # get marginal effects
  pdf <- ifelse(dist=="probit",
                mean(dnorm(predict(x, type = "link"))),
                mean(dlogis(predict(x, type = "link"))))
  marginal.effects <- pdf*coef(x)
  # start bootstrap
  bootvals <- matrix(rep(NA,boot*length(coef(x))), nrow=boot)
  set.seed(1111)
  for(i in 1:boot){
    samp1 <- data[sample(1:dim(data)[1],replace=T,dim(data)[1]),]
    x1 <- glm(modform, family=binomial(link=dist),samp1)
    pdf1 <- ifelse(dist=="probit",
                   mean(dnorm(predict(x, type = "link"))),
                   mean(dlogis(predict(x, type = "link"))))
    bootvals[i,] <- pdf1*coef(x1)
  }
  res <- cbind(marginal.effects,apply(bootvals,2,sd),marginal.effects/apply(bootvals,2,sd))
  if(names(x$coefficients[1])=="(Intercept)"){
    res1 <- res[2:nrow(res),]
    res2 <- matrix(as.numeric(sprintf(paste("%.",paste(digits,"f",sep=""),sep=""),res1)),nrow=dim(res1)[1])
    rownames(res2) <- rownames(res1)
  } else {
    res2 <- matrix(as.numeric(sprintf(paste("%.",paste(digits,"f",sep=""),sep="")),nrow=dim(res)[1]))
    rownames(res2) <- rownames(res)
  }
  colnames(res2) <- c("marginal.effect","standard.error","z.ratio")
  return(res2)
}
```

