 ---
title: "Project 2"
output:
  word_document: default
  html_notebook: default
---
 
 
Splitting out test. TelcoXN is TelcoX converted to numerical in excel.

```{r echo=FALSE}

library(car)
#library(caret)
library(caTools)
library(ggplot2)
library(gridExtra)
library(leaps)
library(MASS)
library(pls)
library(plyr)
library(randomForest)
library(wesanderson)


Telco<-read.csv('TelcoXNlogALL.csv')
#Telco<-read.csv('TelcoXXN.csv')
trainset = subset(Telco, Telco$sample == TRUE)
testset  = subset(Telco, Telco$sample == FALSE)
trainset <-trainset[c(-24)]
trainset <-testset[c(-24)]
summary(Telco)
```

Logistic Model

```{r echo=FALSE}
LogisticModel <- glm(as.factor(Churn) ~ .,family=binomial(link="logit"),data=trainset)
summary(LogisticModel)
anova(LogisticModel, test="Chisq")
```

AIC Selection 

```{r echo=FALSE}
mean_train<-apply(trainset, 2, mean)
var_train<-apply(trainset, 2, var)

train <- t((t(trainset)-mean_train)/sqrt(var_train))
apply(train, 2, mean)
apply(train, 2, var)

dat.train<-data.frame(train, Churn=trainset$Churn)
dat.train<-dat.train[c(-23)]

##	NEED TO APPLY TRAINING MEAN AND STDEV TO STANDARDIZE TEST SET!!  ##
test <- t((t(testset)-mean_train)/sqrt(var_train))
dat.test <- data.frame(test, Churn=testset$Churn)
apply(test, 2, mean)
apply(test, 2, var)

	LogisticModel.int <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="logit"), data=dat.train)
	LogisticModel.full <- glm(as.factor(Churn.1) ~ ., family=binomial(link="logit"),  data=dat.train)
```

Stepwise Selection AIC

```{r echo=FALSE}
stepAIC(LogisticModel.int, direction="both",
             scope=list(lower=LogisticModel.int, upper= LogisticModel.full))
```

Logistic AIC Model

```{r echo=FALSE}
LogisticModelAIC <- glm(formula = as.factor(Churn) ~ TenureLog + Contract + ECheck + 
    PaperlessBilling + TechSupport + OnlineSecurity + One.Year + 
    PhoneService + MonthlyCharges, family = binomial(link = "logit"), data=trainset)
summary(LogisticModelAIC)
anova(LogisticModelAIC, test="Chisq")

fitted.resultsLogisticAIC <- predict(LogisticModelAIC,newdata=testset,type='response')
fitted.resultsLogisticAIC <- ifelse(fitted.resultsLogisticAIC > 0.5,1,0)
misClasificErrorLogisticAIC <- mean(fitted.resultsLogisticAIC != testset$Churn)
print(1-misClasificErrorLogisticAIC)
table(testset$Churn, fitted.resultsLogisticAIC > 0.5)
exp(cbind(OR=coef(LogisticModelAIC), confint(LogisticModelAIC)))
```

Stepwise Selection BIC

```{r echo=FALSE}
stepAIC(LogisticModel.int, direction="both", k=log(1378),
             scope=list(lower=LogisticModel.int, upper= LogisticModel.full), criterion = "BIC")
```

Logistic BIC Model

```{r echo=FALSE}
LogisticModelBIC <- glm(as.factor(Churn) ~ TenureLog + DSL + Contract + 
    ECheck + PaperlessBilling + TechSupport + OnlineSecurity, 
    family = binomial(link = "logit"),data=trainset)
summary(LogisticModelBIC)
anova(LogisticModelBIC, test="Chisq")

fitted.resultsLogisticBIC <- predict(LogisticModelBIC,newdata=testset,type='response')
fitted.resultsLogisticBIC <- ifelse(fitted.resultsLogisticBIC > 0.5,1,0)
misClasificErrorLogisticBIC <- mean(fitted.resultsLogisticBIC != testset$Churn)
print(1-misClasificErrorLogisticBIC)
table(testset$Churn, fitted.resultsLogisticBIC > 0.5)
exp(cbind(OR=coef(LogisticModelBIC), confint(LogisticModelBIC)))
```

Probit Model

```{r echo=FALSE}
ProbitModel <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="probit"),data=dat.train)
summary(ProbitModel)
anova(ProbitModel, test="Chisq")
```

AIC Selection 

```{r echo=FALSE}
ProbitModel.int <- glm(as.factor(Churn.1) ~ 1, family=binomial(link="probit"),data=dat.train)
ProbitModel.full <- glm(as.factor(Churn.1) ~ ., family=binomial(link="probit"),data=dat.train)
```

Stepwise Selection AIC

```{r echo=FALSE}
stepAIC(ProbitModel.int, direction="both",
             scope=list(lower=ProbitModel.int, upper= ProbitModel.full))
```

Probit Model AIC

```{r echo=FALSE}
ProbitModelAIC <- glm(Churn ~ TenureLog + DSL + Contract + 
    ECheck + PaperlessBilling + TechSupport + OnlineSecurity + 
    StreamingMovies + One.Year + PhoneService + MultipleLines + 
    StreamingTV + SeniorCitizen,  family=binomial(link="probit"),data=trainset)
summary(ProbitModelAIC)
anova(ProbitModelAIC, test="Chisq")

fitted.resultsProbitAIC <- predict(ProbitModelAIC,newdata=testset,type='response')
fitted.resultsProbitAIC <- ifelse(fitted.resultsProbitAIC > 0.5,1,0)
misClasificErrorProbitAIC <- mean(fitted.resultsProbitAIC != testset$Churn)
print(1-misClasificErrorProbitAIC)
table(testset$Churn, fitted.resultsProbitAIC > 0.5)
exp(cbind(OR=coef(ProbitModelAIC), confint(ProbitModelAIC)))
```

Stepwise Selection BIC

```{r echo=FALSE}
stepAIC(ProbitModel.int, direction="both", k=log(1378),
             scope=list(lower=ProbitModel.int, upper= ProbitModel.full), criterion = "BIC")
```

Probit BIC

```{r echo=FALSE}
ProbitModelBIC <- glm(as.factor(Churn) ~  TenureLog + DSL + Contract + 
    ECheck + PaperlessBilling + TechSupport, family=binomial(link="probit"),data=trainset)
summary(ProbitModelBIC)
anova(ProbitModelBIC, test="Chisq")

fitted.resultsProbitBIC <- predict(ProbitModelBIC,newdata=testset,type='response')
fitted.resultsProbitBIC <- ifelse(fitted.resultsProbitBIC > 0.5,1,0)
misClasificErrorProbitBIC <- mean(fitted.resultsProbitBIC != testset$Churn)
print(1-misClasificErrorProbitBIC)
table(testset$Churn, fitted.resultsProbitBIC > 0.5)
exp(cbind(OR=coef(ProbitModelBIC), confint(ProbitModelBIC)))
```

Loading Factored Data Set for Random Forest

```{r echo=FALSE}
Telco<-read.csv('TelcoX.csv')
trainset = subset(Telco, Telco$sample == TRUE)
testset  = subset(Telco, Telco$sample == FALSE)
trainset <-trainset[c(-24)]
trainset <-testset[c(-24)]
summary(Telco)
```

Random Forest

```{r eval=FALSE, include=FALSE}

RandomForestMod <- randomForest(Churn ~., data = trainset)
print(RandomForestMod)
RandomForestPredict <- predict(RandomForestMod, testset)
plot(RandomForestMod)
varImpPlot(RandomForestMod, sort=T, n.var = 10, main = 'Top 10 Feature Importance')
RandomForestTune <- tuneRF(trainset[, -23], trainset[, 23], stepFactor = 0.5, plot = TRUE, ntreeTry = 200, trace = TRUE, improve = 0.05)
```

Refit
```{r eval=FALSE, include=FALSE}
RandomForestMod.2 <- randomForest(Churn ~., data = trainset, ntree = 200, mtry = 2, importance = TRUE, proximity = TRUE)
print(RandomForestMod.2)
pred_rf_new <- predict(RandomForestMod.2, testset)
testset$Churn<-as.factor(testset$Churn)

varImpPlot(RandomForestMod.2, sort=T, n.var = 10, main = 'Top 10 Feature Importance')
```

Compare
```{r}
print(LogisticModelAIC)
print ("Logistic AIC")
print(1-misClasificErrorLogisticAIC)
table(testset$Churn, fitted.resultsLogisticAIC > 0.5)
exp(cbind(OR=coef(LogisticModelAIC), confint(LogisticModelAIC)))
print(LogisticModelBIC)
print ("Logistic BIC")
print(1-misClasificErrorLogisticBIC)
table(testset$Churn, fitted.resultsLogisticBIC > 0.5)
exp(cbind(OR=coef(LogisticModelBIC), confint(LogisticModelBIC)))
print(ProbitModelAIC)
print ("Probit AIC")
print(1-misClasificErrorProbitAIC)
table(testset$Churn, fitted.resultsProbitAIC > 0.5)
exp(cbind(OR=coef(ProbitModelAIC), confint(ProbitModelAIC)))
print(ProbitModelBIC)
print ("Probit BIC")Vie
print(1-misClasificErrorProbitBIC)
table(testset$Churn, fitted.resultsProbitBIC > 0.5)
exp(cbind(OR=coef(ProbitModelBIC), confint(ProbitModelBIC)))

```

```{r eval=FALSE, include=FALSE}
LogisticModelTen <- glm(Churn ~ TenureCat.00.06,family=binomial(link="logit"),data=trainset)
summary(LogisticModelTen)
anova(LogisticModelTen, test="Chisq")

fitted.resultsLogisticTen <- predict(LogisticModelTen,newdata=testset,type='response')
fitted.resultsLogisticTen <- ifelse(fitted.resultsLogisticTen > 0.5,1,0)
misClasificErrorLogisticTen <- mean(fitted.resultsLogisticTen != testset$Churn)
print(1-misClasificErrorLogisticTen)
table(testset$Churn, fitted.resultsLogisticTen > 0.5)
exp(cbind(OR=coef(LogisticModelTen), confint(LogisticModelTen)))
ProbitModelTen <- glm(Churn ~ TenureCat.00.06,family=binomial(link="probit"),data=trainset)
summary(ProbitModelTen)
anova(ProbitModelTen, test="Chisq")

fitted.resultsProbitTen <- predict(ProbitModelTen,newdata=testset,type='response')
fitted.resultsProbitTen <- ifelse(fitted.resultsProbitTen > 0.5,1,0)
misClasificErrorProbitTen <- mean(fitted.resultsProbitTen != testset$Churn)
print(1-misClasificErrorProbitTen)
table(testset$Churn, fitted.resultsProbitTen > 0.5)
exp(cbind(OR=coef(ProbitModelTen), confint(ProbitModelTen)))
```

